{Good covers and algebras on conically smooth spaces}

### 2025-08-21 paperversion/paper.tex
localities section, clean part

\newcommand{\R}{\mbb{R}}
\newcommand{\Imm}{\mathrm{Im}}
\newcommand{\id}{{\mathrm{id}}}
\newcommand{\colim}{\mathrm{colim}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\dfnt}{\bfseries \itshape}
\newcommand{\hyph}{{\mbox{-}}}
\newcommand{\Bred}{\mathcal{B}\mbox{-}\mathrm{red}}
\newcommand{\Yred}{Y\mbox{-}\mathrm{red}}
\newcommand{\Bopen}{\mathcal{B}\mbox{-}\mathrm{open}}
\newcommand{\Snglr}{\mathcal{S}\mathrm{nglr}}
\newcommand{\bighrule}{\vspace{\baselineskip} \hrule \hrule \hrule\vspace{\baselineskip}}
\newcommand{\solidone}{\mathbf{s}\ast_1} 
\newcommand{\Vinj}{{\mscc{V}^{\mathrm{inj}}}}
\newcommand{\Vhook}{\mscc{V}^{\hookrightarrow}}
\newcommand{\Vsim}{{\mscc{V}^{\simeq}}}
\newcommand{\Vlhook}{\mscc{V}^{\hookleftarrow}}
\newcommand{\TB}{T^{\mathcal{B}}}
\newcommand{\EX}{{\mathbf{Ex}}}
\newcommand{\Disk}{{\mathcal{D}\mathrm{isk}}}
\newcommand{\scB}{{\mathcal{B}}}
\newcommand{\OB}{{\mathbb{O}^{\mathcal{B}}}}
\newcommand{\Mnf}{{\mscc{M}\mathrm{nf}}}
\newcommand{\sfr}{{\mathbf{s}\ast}}
\newcommand{\solid}{\mathbf{s}}
\newcommand{\Bord}{{\mathrm{Bord}}}
\newcommand{\BM}{{\mathcal{B}\mathbf{M}}}
\newcommand{\pt}{{\mathrm{pt}}}
\newcommand{\falc}{{\mathrm{FA}^{\mathrm{lc}}}}
\newcommand{\stfr}{{\mathbf{st}\ast}}
\newcommand{\Tang}{{\mathcal{T}\mathrm{ang}}}
\newcommand{\opp}{{\mathrm{op}}}
\newcommand{\Opp}{{\mathrm{Op}}}
\newcommand{\Vsur}{{\mathcal{V}^{\twoheadrightarrow}}}
\newcommand{\EN}{{\mathbf{En}}}
\newcommand{\codim}{{\mathrm{codim}\,}}
\newcommand{\red}{{\text{-}\mathrm{red}}}
\newcommand{\Vect}{{\mathcal{V}}}
\newcommand{\Cinfty}{\mscc{C}\mathrm{at}_{\infty}}
\newcommand{\Sp}{{\mathcal{S}\mathrm{p}}}
\newcommand{\BhookO}{{\mathcal{B}^{\hookrightarrow}\mathrm{O}}}
\newcommand{\EhookO}{{\mathcal{E}^{\hookrightarrow}\mathrm{O}}}
\newcommand{\purp}{\color{purple}}
\newcommand{\Eop}{{\mathcal{E}^{\mathrm{op}}}}
\newcommand{\E}{{\mathcal{E}}}
\newcommand{\Tw}{{\mathrm{Tw}}}
\newcommand{\Map}{{\mathrm{Map}}}
\newcommand{\gpdinf}{{\mathcal{G}\mathrm{pd}_{\infty}}}
\newcommand{\cdon}{\[\begin{tikzcd}}
\newcommand{\cdoff}{\end{tikzcd}\]}
\newcommand{\ncdon}{\begin{equation}\begin{tikzcd}}
\newcommand{\ncdoff}{\end{tikzcd}\end{equation}}
\newcommand{\OO}{{\mathrm{O}}}
\newcommand{\pbarrow}{\ar[dr,phantom,"\ulcorner" very near start]}
\newcommand{\Gr}{{\mathrm{Gr}}}
\newcommand{\arrowedruleron}{{\vspace{5pt}{\purp\hrule\hrule\hrule}
\begin{center}\purp
	$\downarrow$
\end{center}}}
\newcommand{\arrowedruleroff}{{\begin{center}\purp
	$\uparrow$
\end{center}
\vspace{5pt}{\purp\hrule\hrule\hrule}}}
\newcommand{\blue}{\color{blue}}
\newcommand{\Sing}{{\mathrm{Sing}}}
\newcommand{\Bbox}{\mathcal{B}^{\oplus}}
\newcommand{\bbox}{B^{\oplus}}
\newcommand{\bboxop}{B^{\oplus}_{\opp}}
\newcommand{\Nerve}{{\mathrm{N}}}
\newcommand{\Ndelta}{\mathrm{N}^{\mbf{\Delta}}}
\newcommand{\Nhc}{\mathrm{N}^{\mathrm{hc}}}
\newcommand{\sSet}{\mathrm{sSet}}
\newcommand{\Cdelta}{{\mathcal{C}\mathrm{at}_{\mbf{\Delta}}}}
\newcommand{\pSh}{\mathrm{pSh}}
\newcommand{\EEx}{\mathbf{EX}}
\newcommand{\Pnsim}{\mscc{P}^{\nsim}}
\newcommand{\Phat}{\mscc{P}^{\Delta}}
\newcommand{\Pbox}{\mscc{P}^{\Box}}
\newcommand{\Nhat}{\widehat{\mathcal{N}}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Path}{\mathrm{Path}}
\newcommand{\Tangent}{\mathrm{T}}
\newcommand{\Normal}{\mathrm{N}}
\newcommand{\vfr}{\mathrm{vfr}}
\newcommand{\hty}{\mathrm{h}}
\newcommand{\evv}{\mathrm{ev}}
\newcommand{\Ar}{\mathrm{Ar}}
\newcommand{\inc}{$\infty$-category}
\newcommand{\btu}{\bigtriangleup}
\makeatletter
\newcommand{\btd}{\mathord{\mathpalette\raise@half\bigtriangledown}}
\newcommand\raise@half[2]{%
  \raisebox{.9\depth}{$\m@th#1#2$}%
}
\makeatother
\newcommand{\ashrk}{\text{\textexclamdown}}
\newcommand{\dash}{\mbox{-}}
\newcommand{\cat}[2]{\mscc{#1}\mathrm{#2}}
\newcommand{\htimes}{\times^{\mathrm{h}}}

\newcommand{\spans}{\mscc{S}^{\mrm{sp}}}
\newcommand{\OEEx}{\overrightarrow{\EEx}}
\newcommand{\Ssp}{\mscc{S}^{\mrm{sp}}}
\newcommand{\ocat}[1]{\mathrm{#1}}
\newcommand{\Ctop}{\mscc{C}\mrm{at}_{\mrm{Top}}}
\newcommand{\Tame}{\Hom^{t}}
\newcommand{\tame}{\tau}
\newcommand{\Unzip}{\mrm{Unzip}}

@@

>>>>

\newcommand{\R}{\mbb{R}}
\DeclareMathOperator{\Imm}{Im}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\dfnt}{\bfseries \itshape}
\newcommand{\hyph}{{\mbox{-}}}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Tangent}{\mathrm{T}}
\newcommand{\Normal}{\mathrm{N}}
\newcommand{\evv}{\mathrm{ev}}  
\DeclareMathOperator{\Unzip}{Unzip}
\DeclareMathOperator{\Link}{Link}

@@

\section{Localities of the full unzip}

\begin{definition}
    $S_X\subset X$.
\end{definition}

\begin{proposition}\label{7GBVGBA}
    $S_X\subset X$ proper constructible bundle with $\Unzip_{S_X}(X)\cong\Unzip(X)$ and $\Link_{S_X}(X)=\partial\Unzip(X)$.
\end{proposition}

\begin{lemma}\label{DNFREG0}
    {\color{gray}Locally finite good cover on $S_X$. (?)} {\bf unnecessary - second-countability implies more than paracompactness - see [Lee, Smooth, Thm 1.15]}
\end{lemma}

\begin{lemma}\label{K52SWOM}
    Let $X$ be a smooth manifold with corners. Then for every boundary collar $I\colon \R_{\geq0}\times \partial X\hookrightarrow X$ there exists a homeomorphism
    \[
        \alpha_I\colon X^+\xrightarrow{\cong}\R_{\geq0}\times X
    \]
    where $X^+=\bigcup_{r\in\R_{\geq0}}[0,r]\times\partial X\cup_{\{r\}\times\partial X}X$.
\end{lemma}
\begin{proof}
    Let $I\colon\R_{\geq0}\times\partial X\hookrightarrow X$ be a collar, which is a homeomorphism onto its image. We have $X=I(\R_{\geq0}\times \partial X)\cup_{I((0,\infty)\times\partial X)}X^\circ$. Similarly, for each $r$, we have a diffeomorphism 
    \[
        \alpha_r\colon X\to X\smallsetminus I([0,r)\times\partial X)=I([r,\infty)\times\partial X)\cup_{I((r,\infty)\times\partial X)}X\smallsetminus I([0,r]\times\partial X)
    \]
    given by $I(t,q)\mapsto I(t+r,q)$ on $I(\R_{\geq0}\times\partial X)$ and by the identity on $X\smallsetminus \Imm(I)$. We suppress the dependence on $I$ in notation. We obtain a well-defined homeomorphism 
    \[
        I\cup\alpha_r\colon [0,r]\times\partial X\cup_{\{r\}\times \partial X}X\to X,
    \]
    well-defined since $\alpha_r(q)=\alpha_r(I(0,q))=I(r,q)$ for $q\in\partial X$, and thereupon, writing $X^{+r}=[0,r]\times\partial X\cup_{\{r\}\times \partial X}X$, the bijection 
    \begin{align*}
        &\alpha_I\colon X^+\to \R_{\geq0}\times X,\\
        &\alpha|_{X^{+r}}=\{r\}\times I\cup\alpha_r.
    \end{align*}
    We equip $X^+$ with the induced topology, promoting $\alpha$ to a homeomorphism.
\end{proof}

\begin{lemma}\label{DGSR46V}
    Let $X$ be a smooth manifold with corners. Then there is a homeomorphism $\R_{\geq0}\times \partial(\R_{\geq0}\times X)\cong\R_{\geq0} \times X$. Consequently, there is a homeomorphism
    \[
        \Unzip_{C(L)}(C(Z))\cong\R_{\geq0}\times\Link_{C(L)}(C(Z))
    \] 
    for $L=S_Z$.
\end{lemma}

\begin{proof}
    Using \Cref{K52SWOM} it suffices to provide a homeomorphism
    \[
        \phi\colon\R_{\geq0}\times\partial(\R_{\geq0}\times X)\to\bigcup_{r\in\R_{\geq0}}[0,r]\times\partial X\cup_{\{r\}\times\partial X}X.
    \]
    Noting 
    \[
        \partial(\R_{\geq0}\times X)=\{0\}\times X\cup_{\{0\}\times \partial X}\R_{\geq0}\times\partial X,
    \] 
    we define $\phi$ to be the following map: 
    \begin{align*}
        \R_{\geq0}\times\{0\}\times X\ni (t,0,x)&\mapsto x\in X\subset[0,t]\times \partial X\cup_{\{t\}\times\partial X}X\\
        \R_{\geq0}\times\R_{\geq0}\times\partial X\ni(t,s,q)&\mapsto (t,q)\in[0,t+s]\times\partial X.
    \end{align*}
    This map and its inverse $\phi^{-1}$ given by
    \begin{align*}
        [0,r]\times\partial X \ni (t,q) &\mapsto (t,r-t,q)\in \R_{\geq0}\times\R_{\geq0}\times\partial X\\
        [0,r]\times\partial X\cup_{\{r\}\times\partial X}X\supset X\ni x&\mapsto (r,0,x)\in\R_{\geq0}\times\{0\}\times X
    \end{align*}
    are well-defined and continous. Note that $\phi$ does not nepend on a collar.

    The second statement is the special case where $X=\Unzip_L(Z)$ using \Cref{7GBVGBA} and that $\Unzip_{C(L)} C(Z)=\R_{\geq0}\times \Unzip_L(Z)$ and $\Link_{C(L)}C(Z)=\partial\Unzip_{C(L)}(C(Z))$.  
\end{proof}

\begin{remark}
    In the situation of \Cref{K52SWOM} we will regard $X^+$ as a smooth manifold with corners with respect to the smooth structure induced by $\alpha_I$. Up to equivalence, this structure does not depend on the choice of collar. Similarly, in the situation of \Cref{DGSR46V} we will regard $\R_{\geq0}\times\Link_{C(L)}C(Z)$ as a smooth manifold with corners, tautologically diffeomorphic to $\Unzip_{C(L)}C(Z)$ with respect to the induced smooth structure.
\end{remark}

\begin{construction}\label{O6BEXS3}
    Let $X$ be a smooth manifold with corners of dimension $n$, let $\{(U,\phi_U)\}$ a cover of $X$ by coordinate neighbourhoods where each $\phi_U\colon\R^{n-c_U}\times\R^{c_U}_{\geq0}$ is a homeomorphism, and let $\{\rho_U\colon X\to[0,1]\}$ be a partition of unity subordinate to this cover. Recall that a collar $I=I(\{U,\phi_U,\rho_U\})\colon \R_{\geq0}\times\partial X\hookrightarrow X$ is then constructed by defining to be the flow along the nowhere-vanishing inward-pointing vector field $V=\sum\rho_U V_U$ where, in local coordinates, $V_U=\sum_{1\leq i\leq c_U}\partial_i$ where $\{\partial_i\}$ is the standard basis of $\Tangent_0\R^{c_U}_{\geq0}\subset\Tangent_0(\R^{n-c_U}\times\R^{c_U}_{\geq0})$.

    Let $X$ and $I=I_{\{U,\phi_U,\rho_U\}}$ be as above. Then there is a canonically induced a collar 
    \[
        I^+=I(\{\R_{\geq0}\times U,\id_{\R_{\geq0}}\times\phi_U,\mrm\rho_U\circ\mrm{pr}_X\})\colon \R_{\geq0}\times\partial(\R_{\geq0}\times\partial X)\hookrightarrow \R_{\geq0}\times X
    \] 
    on $\R_{\geq0}\times X$, where $\mrm{pr}_X\colon \R_{\geq}\times X\to X$ is the coordinate projection. It is the flow along the vector field $V^+=\sum(\rho_U\circ\mrm{pr}_X)\cdot V_U^+$ where $V_U^+=\partial_s+V_U$ where $\partial_s$ is the standard basis of $\Tangent_0\R_{\geq0}\subset\Tangent_0(\R_{\geq0}\times\R^{n-c_U}\times\R^{c_U}_{\geq0})$.
\end{construction}

\begin{lemma}
    Let $X$ be a smooth manifold with corners and let $I^+\colon\R_{\geq0}\times \partial(\R_{\geq0}\times\partial X)\hookrightarrow\R_{\geq0}\times X$ be as in \Cref{O6BEXS3}. Then 
    \[
        I^+=\alpha_I\circ\phi
    \]
    where $\alpha_I$ is as in \Cref{K52SWOM} and $\phi$ is as in the proof of \Cref{DGSR46V}.
\end{lemma}
\begin{proof}
    We observe the restrictions 
    \begin{align*}
        \R_{\geq0}\times\{0\}\times X&\xrightarrow{\alpha_I\circ\phi}\R_{\geq0}\times X\\
        (t,0,x)&\mapsto \begin{cases}
            (t,I(t_x+t,q)), & x=I(t_x,q)\\
            (t,x), & x\in X\smallsetminus\Imm(I)
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        \R_{\geq0}\times\R_{\geq0}\times\partial X&\xrightarrow{\alpha_I\circ \phi} \R_{\geq0} \times X\\
        (t,s,q)&\mapsto (t+s,I(t,q)).
    \end{align*}
    Both maps are the flow (for time $t$) along the vector field $V^+=\sum(\rho_U\circ\mrm{pr}_X)\cdot(\partial_s+V_U)$.
\end{proof}

In the following, $\mbb{D}^n\subset\R^n$ denotes the unit open $n$-disk and $C^{<1}(Z)=\ast\amalg_{\{0\}\times Z}[0,1)\times Z$.

\begin{definition}
    We say an embedded basic $\phi\colon \R^k\times C(Z)\hookrightarrow X$ in a conically smooth space $X$ is \emph{extendable} if there exists an embedding $\widehat{\phi}\colon\R^n\times C(Z)\hookrightarrow X$ such that $\phi$ factors as $\phi\colon\R^{k}\times C(Z)\to \mbb{D}^n\times C^{<1}(Z)\hookrightarrow \R^n\times C^{<1}(Z)\xhookrightarrow{\widehat{\phi}}X$ where the first map is the isomorphism given by the cartesian product of the isomorphisms $\R^n\to\mbb{D}^n$, $x\mapsto \frac{x}{|x|+1}$ and $C(Z)\to C^{<1}(Z)$, $(t,z)\mapsto (\frac{t}{t+1},z)$. 
\end{definition}

\begin{definition}
    Suppose $\mcal{U}$ is a cover of a topological space $X$ which is closed under finite intersections. We say $\mcal{U}$ is \emph{generated} by a cover $\mcal{V}$ and write $\mcal{U}=\langle\mcal{V}\rangle$ if every member of $\mcal{U}$ is a finite intersection of members of $\mcal{V}$.
\end{definition}

\begin{lemma}\label{2978BNV}
    Every smooth manifold $M$ has a good cover $\mcal{U}$ which is generated by extendable basics.
\end{lemma}
\begin{proof}
    Equip $M$ with a riemannian metric. We can put $\mcal{U}=\langle\mcal{V}\rangle$ for $\mcal{V}=\{D_p\}_{p\in M}$ where $D_p$ is the convex disk which is the interior of the image of a ball in $\Tangent_p M$ under the exponential map, with radius strictly smaller than the radius of injectivity.
\end{proof}

\begin{lemma}
    Suppose $U\subset C(Z)$ be conically smooth basics with $S_{C(Z)}\cong U$, and suppose that $U\cong C(L)$ is extendable. Let $\pi\colon \Link(C(Z))|_{U}\to U$ denote the link projection of $\Unzip (C(Z))$ over $U$. Then there is an isomorphism
    \[
        \partial\overline{\pi^{-1}U}\cong \Link_L(Z)
    \]
    and an induced conically smooth collar 
    \[
        (0,1]\times\partial\overline{\pi^{-1}U}\hookrightarrow \overline{\pi^{-1}U}
    \]
    which is a refinement onto its image.
\end{lemma}
\begin{proof}
    Up to isomorphism we have that $U=C^{<1}(L)\subset C^{<1}(Z)\subset C(Z)$ is induced by the inclusion $L=S_Z\subset Z$. Abbreviating $S=S_{C(Z)}$, the inclusion of $U$ factors as $U\subset S=C(L)$ . Now, using \Cref{7GBVGBA} we have $\Unzip C(Z)=\Unzip_{S}C(Z)=\R_{\geq0}\times\Unzip_L Z$ and so 
    \begin{align*}
        \Unzip C(Z)|_{U}&=\Link_{C(L)}C(Z)|_{C^{<1}(L)}\\
        &=\{0\}\times \Unzip_L Z\cup_{\{0\}\times\Link_LZ}[0,1)\times\Link_L Z\\
    \end{align*}
    since the projection $\pi\colon\Link_{C(L)}C(Z)=\{0\}\times\Unzip_L Z\cup_{\{0\}\times\Link_LZ}\R_{\geq0}\times \Link_L Z\to C(L)=\ast\amalg_{\{0\}\times L}\R_{\geq0}\times L$ is given by mapping all of $\{0\}\times\Unzip_L Z$ to $\ast$ and on $\R_{\geq0}\times \Link_LZ$ by $\id_{\R_{\geq0}}\times\pi'$ where $\pi'\colon \Link_LZ\to L$ is the link projection.
    Thus 
    \[
        \pi^{-1}\overline{U}=\pi^{-1}C^{\leq 1}(U)=\{0\}\times\Unzip_LZ\cup[0,1]\times\Link_LZ 
    \]
    and consequently 
    \[
        \pi^{-1}\partial\overline{U}=\pi^{-1}\{1\}\times L=\{1\}\times\Link_L Z,
    \]
    proving the first claim. The collar is immediate.
\end{proof}

\begin{example}

\end{example}

\begin{corollary}

\end{corollary}
